\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-22 sections/results.tex
Add: Supplementary section for seqtime data

  Similar to the previous steps of the pipeline, where were we evaluated the performance of methods on mock datasets, we can evaluate the network inference algorithms and the final consensus network using synthetic interaction data.
  For this purpose, we generated synthetic interaction data using the ``NorTA''[ref] and ``seqtime''[ref] methods (see Methods), which have been previously used for benchmarking network inference methods.
  For each method, an \ac{otu} counts table is generated based on the selected interaction network topology and properties.
  This counts table is used as the input to the \ac{micone} pipeline to generate predicted associations.
  The interaction network used to generate the counts table is used as the source of true interactions to calculate the precision and sensitivity for each network inference algorithm for the NorTA datasets (Figure \ref{fig:figure6}).
  Each point in the scatter plot represents a network with different input network topology and OTU abundance distributions.
  Overall, we see that the scaled-sum method for a parameter value of 0.5 performs the best in terms of average precision ($0.985$).
  Among the individual inference methods, we observe that \ac{spieceasi} has the best average precision ($0.944$)
  The goal of the consensus network algorithms is to increase the precision of the resultant consensus network by removing edges that are either not present in most of the inference methods or whose association strength is low.
  From Figure \ref{fig:figure6} we can confirm that the consensus algorithm, especially the scaled-sum method, does indeed produce networks with more precision, but as a consequence the sensitivity of the networks is reduced.
  Therefore, the consensus networks provide the means to obtain a short list of associations that would have a high probability of being present in the real interaction network.
  This small set of associations could be further tested and validated experimentally to verify their plausibility.

  % TODO: Supplementary work: Figure S7
  The precision and sensitivity graphs on the seqtime data can be found in the Supplementary section.

@@

  Figure~\ref{fig:figure7}A shows the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  These results indicate that the biggest rewiring in networks occur when the reference database or the network inference algorithm are changed.
  % TODO: Show proof??
  The filtering in the \ac{OP} step when turned off also adds a large number of new nodes, but the edges between the common nodes (with the default network) are fairly conserved.
  % TODO: Say that this shows how important the consensus network is in the whole pipeline
  Furthermore, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ni} steps are changed.
  This result is different from that observed in Figure~\ref{fig:figure2} since in this particular analyses all the steps other than the \ac{ni} step have the consensus algorithm applied to them, which drastically reduces the edges in the graph that have lower probabilities.
  This result reinforces the importance of the consensus network in increasing the robustness of the inferred networks to different processing methods.
  Figure~\ref{fig:figure7}C shows the co-occurrence networks inferred for the healthy subjects (control) and autistic subjects in the fecal microbiome transplant study~\cite{Kang2017}.
  These consensus networks were generated using the default tools and parameters from Table~\ref{tab:default_options}.

>>>>

  Similar to the previous steps of the pipeline, where were we evaluated the performance of methods on mock datasets, we can evaluate the network inference algorithms and the final consensus network using synthetic interaction data.
  For this purpose, we generated synthetic interaction data using the ``NorTA''~\cite{Kurtz2015} and ``seqtime''~\cite{faustSignaturesEcologicalProcesses2018} methods (see Methods), which have been previously used for benchmarking network inference methods.
  For each method, an \ac{otu} counts table is generated based on the selected interaction network topology and properties.
  This counts table is used as the input to the \ac{micone} pipeline to generate predicted associations.
  The interaction network used to generate the counts table is used as the source of true interactions to calculate the precision and sensitivity for each network inference algorithm for the NorTA datasets (Figure \ref{fig:figure6}).
  Each point in the scatter plot represents a network with different input network topology and OTU abundance distributions.
  Overall, we see that the scaled-sum method for a parameter value of 0.5 performs the best in terms of average precision ($0.985$).
  Among the individual inference methods, we observe that \ac{spieceasi} has the best average precision ($0.944$)
  The goal of the consensus network algorithms is to increase the precision of the resultant consensus network by removing edges that are either not present in most of the inference methods or whose association strength is low.
  From Figure \ref{fig:figure6} we can confirm that the consensus algorithm, especially the scaled-sum method, does indeed produce networks with more precision, but as a consequence the sensitivity of the networks is reduced.
  Therefore, the consensus networks provide the means to obtain a short list of associations that would have a high probability of being present in the real interaction network.
  This small set of associations could be further tested and validated experimentally to verify their plausibility.

  Furthermore, we also find that the consensus algorithm performs drastically better in terms of precision (0.820 for scaled-sum method vs. 0.624 for \ac{spieceasi}) in recapturing the orginal interactions in the data.
  The precision and sensitivity graphs on the seqtime data can be found in the Supplementary section (Figure~\ref{fig:figure_s7}).

@@

  Figure~\ref{fig:figure7}A shows the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  These results indicate that the biggest rewiring in networks occur when the reference database or the network inference algorithm are changed.
  % TODO: Show proof??
  The filtering in the \ac{OP} step when turned off also adds a large number of new nodes, but the edges between the common nodes (with the default network) are fairly conserved.
  % TODO: Say that this shows how important the consensus network is in the whole pipeline
  Furthermore, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ni} steps are changed.
  This shows us that not only does the consensus help reconcile the variability in the edges due to multiple network inference algorithms, it also helps reconcile the variability to the other steps of the pipline as well.
  This result is different from that observed in Figure~\ref{fig:figure2} since in this particular analyses all the steps other than the \ac{ni} step have the consensus algorithm applied to them, which drastically reduces the edges in the graph that have lower probabilities.
  This result reinforces the importance of the consensus network in increasing the robustness of the inferred networks to different processing methods.
  Figure~\ref{fig:figure7}C shows the co-occurrence networks inferred for the healthy subjects (control) and autistic subjects in the fecal microbiome transplant study~\cite{Kang2017}.
  These consensus networks were generated using the default tools and parameters from Table~\ref{tab:default_options}.

### 2022-04-22 sections/supplementary.tex
Add: Supplementary section for seqtime data

  \subsection*{Performance of consensus network on NorTA data}

@@

  \subsection*{Performance of consensus network on seqtime data}

@@

  % TODO: Write all these sections
  \subsection*{Performance of network inference algorithms on seqtime data}
  \subsection*{The JSON network format}

  \begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{figureS1.pdf}
  \caption{
    \textbf{Comparison of various denoising and clustering algorithms used in the pipeline}.
    (A, B) Correlation of the abundances of the taxa that are in common between the count matrices created by two different methods.
    (A) The worst correlation (least similar methods) is between open-reference and dada2.
    (B) The best correlation (most similar methods) is between open-reference and denovo.
    (C) A heatmap showing the $\mathrm{R}^2$ of all pairwise comparisons of the methods.
  }
  \label{fig:figureS1}
\end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figureS2.pdf}
    \caption{
      \textbf{Heatmaps showing the weighted and unweighted unifrac distances for the hard palate dataset analysis}.
      (A) weighted unifrac distances and (B) unweighted unifrac distances between the representative sequences generated by different denoising and clustering algorithms.
      These results are in agreement with the stool microbiome dataset.
    }
    \label{fig:figureS2}
  \end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figureS3.pdf}
    \caption{
      \textbf{The distributions of the average weighted UniFrac distance between the expected sequence profile and the calculated sequence profile in the synthetic datasets}.
      We observe no significant difference between the various methods on the synthetic datasets used for this study.
    }
    \label{fig:figureS3}
  \end{figure}

%   \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.9\linewidth]{pdf/all_denoise_reg.pdf}
%     \caption*{All pairwise correlations comparing the similarity between different denoising and clustering methods}
%     \label{fig:figureS4}
%   \end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figureS4.pdf}
    \caption{
      \textbf{(A)} Taxonomy composition of the 20 most abundant genera predicted for the stool microbiome dataset generated using different taxonomy references databases: Greengenes, SILVA and NCBI.
      The legend shows the common and the unique genera among the taxonomy assignments.
  }
    \label{fig:figureS4}
  \end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figureS5.pdf}
    \caption{
      The bray-curtis dissmilarity between the expected taxonomic composition and generated taxonomic composiion for the synthetic datasets.
  }
  \label{fig:figureS5}
  \end{figure}

%   \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{figureS6.pdf}
%     \caption{
%       Calculation of presence threshold that is applied on the OTU table in the OTU processing (OP) step of the pipeline.
%       This presence threhold $p_t$ is dependent on the number of samples in the dataset and the required correlation stength threshold.
%   }
%     \label{fig:figureS6}
%   \end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figureS8.pdf}
    \caption{
      The similarity between the networks generated using the different network inference algorithms for stool dataset (A) and the hard palate dataset (B).
      The similarity between the various methods was found to vary with the dataset used.
  }
    \label{fig:figureS8}
  \end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{pdf/denoise_network.pdf}
    \caption{A network showing union (A) and intersection (B) of networks generated using different denoising and clustering tools on the Stool dataset.}
    \label{fig:figureS5}
  \end{figure}

>>>>

  \subsection*{Performance of alternate consensus network on NorTA data}

    In Figure~\ref{fig:figure_s6} we calculate the consensus network by also taking into account the networks inferred by the Pearson and Spearman methods.
    We see that the consensus networks in this case do not perform as well as those networks that did not incorporate these two algorithms.
    However, we still observe that the consensus network at some parameter values still outperforms the best network inference method (\ac{spieceasi}).

@@

  \subsection*{Performance of network inference algorithms on seqtime data}

    % TODO: Elaborate on this
    In Figure~\ref{fig:figure_s7} we perform the same analysis we did with the NorTA data using the seqtime data.
    We observe that the best performing network inference algorithm is \ac{spieceasi}, but the consensus algorithms, both the scaled-sum and simple voting methods outperform it in terms of precision.
    These results show that the scaled-sum method is much better suited for inferring robust and accurate interactions from count data regardless of the distributions, topologies and number of samples in the data.

@@

  % TODO: Write more about this and link to documentation
  \subsection*{The JSON network format}

    The default format
